### 2020-07-23 manuscript/fig/geometry.tex
dd

% Text Node
\draw (266,132) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \theta $};
% Text Node
\draw (213,25) node [anchor=north west][inner sep=0.75pt]   [align=left] {$V_{w}$};
% Text Node
\draw (388.96,26.91) node [anchor=north west][inner sep=0.75pt]  [rotate=-36.98] [align=left] {$\frac{\partial T}{\partial y}$ = 0};
% Text Node
\draw (545.74,117.2) node [anchor=north west][inner sep=0.75pt]  [rotate=-36.98] [align=left] {$\frac{\partial T}{\partial y}$ = 0};
% Text Node
\draw (412.73,141.96) node [anchor=north west][inner sep=0.75pt]  [rotate=-36.98] [align=left] {$T=0.5$};
% Text Node
\draw (491.57,17.31) node [anchor=north west][inner sep=0.75pt]  [rotate=-36.98] [align=left] {$T=-0.5$};
% Text Node
\draw (232,93) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle x$};
% Text Node
\draw (200,58) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle y$};
% Text Node
\draw (450,109) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\mathbf{g}$};
% Text Node
\draw (492.55,79.36) node [anchor=north west][inner sep=0.75pt]  [rotate=-36.55] [align=left] {$\displaystyle x$};
% Text Node
\draw (439.69,79.19) node [anchor=north west][inner sep=0.75pt]  [rotate=-36.55] [align=left] {$\displaystyle y$};
% Text Node
\draw (511,160) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \theta $};

>>>>

% Text Node
\draw (264,129) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \theta $};
% Text Node
\draw (211,22) node [anchor=north west][inner sep=0.75pt]   [align=left] {$u_{w}$};
% Text Node
\draw (389.16,23.31) node [anchor=north west][inner sep=0.75pt]  [rotate=-36.98] [align=left] {$\frac{\partial T}{\partial y}$ = 0};
% Text Node
\draw (545.94,113.6) node [anchor=north west][inner sep=0.75pt]  [rotate=-36.98] [align=left] {$\frac{\partial T}{\partial y}$ = 0};
% Text Node
\draw (412.94,138.36) node [anchor=north west][inner sep=0.75pt]  [rotate=-36.98] [align=left] {$T=0.5$};
% Text Node
\draw (491.78,13.71) node [anchor=north west][inner sep=0.75pt]  [rotate=-36.98] [align=left] {$T=-0.5$};
% Text Node
\draw (230,90) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle x$};
% Text Node
\draw (198,55) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle y$};
% Text Node
\draw (448,106) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\mathbf{g}$};
% Text Node
\draw (492.73,75.76) node [anchor=north west][inner sep=0.75pt]  [rotate=-36.55] [align=left] {$\displaystyle x$};
% Text Node
\draw (439.87,75.59) node [anchor=north west][inner sep=0.75pt]  [rotate=-36.55] [align=left] {$\displaystyle y$};
% Text Node
\draw (509,157) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \theta $};
% Text Node
\draw (175,203) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont (a)}};
% Text Node
\draw (469,204) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont (b)}};
